Interval Probability and Measurement for Fuzzy Quantum Theories

### 2016-09-19 prob.tex
From: Tai, Yu-Tsung Sent: Monday, September 19, 2016 1:32 To: Ortiz, Gerardo <ortizg@indiana.edu>; 'Amr Sabry (sabry@cs.indiana.edu)' <sabry@cs.indiana.edu>; Hanson, Andrew J. <hansona@indiana.edu> Cc: Liu, Weihua <liuweih@indiana.edu> Subject: RE: ortizg@indiana.edu
Dear all,

I have just verified this week that every classical interval-valued probability measure (IVPM) has a non-empty core when the size of the sample space less or equal to 5… The program for the size of the sample space = 6 is running, but it requires to solve a linear programming (?) with 64 variables and about 815211 condi

The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces}...}

@@

\begin{thm}Consider\emph{ }$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $.
There is a unique interval-valued Born rule~$\bar{\mu}^{B}:\left\{ \ket{\phi}\in\Hilb\middle|\ip{\phi}{\phi}=1\right\} \rightarrow\left(\events\rightarrow\mathscr{I}\right)$
such that:
\begin{itemize}
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}$ is an interval-valued
probability measure.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(\proj{\phi}\right)=\necess$.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(P\right)=\bar{\mu}_{\mathbf{U}\ket{\phi}}^{B}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\qed\end{thm}

>>>>

The other approach might be keep going section~\ref{sec:Quantum-Probability-Spaces},
but try to prove there is a unique interval-valued Born rule with
extra-conditions. I sketched a possible set of conditions, but haven't
verified whether it really works or not...}

@@

\begin{thm}Consider\emph{ }$\mathscr{I}=\left\{ \necess,\imposs,\unknown\right\} $.
There is a unique interval-valued Born rule~$\bar{\mu}^{B}:\left\{ \ket{\phi}\in\Hilb\middle|\ip{\phi}{\phi}=1\right\} \rightarrow\left(\events\rightarrow\mathscr{I}\right)$
such that:
\begin{itemize}
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}$ is an interval-valued
probability measure.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(\proj{\phi}\right)=\necess$.
\item For any pure state~$\ket{\phi}$, $\bar{\mu}_{\phi}^{B}\left(P\right)=\bar{\mu}_{\mathbf{U}\ket{\phi}}^{B}\left(\mathbf{U}P\mathbf{U}^{\dagger}\right)\textrm{ ,}$where
$\mathbf{U}$ is any unitary map, i.e., $\mathbf{U}^{\dagger}\mathbf{U}=\mathbb{1}$. 
\end{itemize}
\qed\end{thm}
\begin{proof}
? 
\end{proof}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
